Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-23 ICLR25/experiments.tex
update

We focus on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer. The bounds for nodes of the first two layers are computed exactly using the full MILP encoding. We report in Table \ref{tab:example1} the average uncertainty of $\MILP_X$ following the choice of the $K$ heaviest neurons for our utility function, vs choosing $K$ nodes from layers $1$ and $2$. We compared with a random choice in the first two layers, and also choice based on strength in \cite{DivideAndSlide}, defined as 
$strength(n) = (UB(n)-LB(n))\cdot |W_{cd}|$, which is thus limited to the previous (2sd hidden layer).

>>>>

We focus on the uncertainty of nodes in the third layers, wrt ReLU nodes in the first and second layer. The bounds for nodes of the first two layers are computed exactly using the full MILP encoding. We report in Table \ref{tab:example1} the average uncertainty of $\MILP_X$ following the choice of the $K$ heaviest neurons for our utility function, vs choosing $K$ nodes from layers $1$ and $2$. We compared with a random choice in the first two layers, and also choice based on strength in \cite{DivideAndSlide}, defined as 
$strength(n) = (\UB(n)-\LB(n))\cdot |W_{cd}|$, which is thus limited to the previous (2sd hidden layer).

### 2024-09-23 ICLR25/valabstraction.tex
update

The crucial factor in such an approach is to {\em select} few opened neurons in $X$ which are the most important for the accuracy. An extreme strategy was adopted in \cite{DivideAndSlide}, where only nodes of the immediate previous layer could be opened, and the measure to choose a neuron $a$ to open to compute the values for neuron $b$ was to consider $|W_{ab}| (UB(a)-LB(a))$. To obtain a more accurate measure, that can also scale to deeper layers and is not limited to open nodes from the immediate previous layer, we first study the LP abstraction.

>>>>

The crucial factor in such an approach is to {\em select} few opened neurons in $X$ which are the most important for the accuracy. An extreme strategy was adopted in \cite{DivideAndSlide}, where only nodes of the immediate previous layer could be opened, and the measure to choose a neuron $a$ to open to compute the values for neuron $b$ was to consider $|W_{ab}| (\UB(a)-\LB(a))$. To obtain a more accurate measure, that can also scale to deeper layers and is not limited to open nodes from the immediate previous layer, we first study the LP abstraction.
